---
title: 'Assignment #2'
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)         # for graphing and data cleaning
theme_set(theme_minimal()) # Lisa's favorite theme
```

## Project ideas

Answer the following questions to start thinking about the project.

-   What are some topics (or a single topic) you are interested in studying from a data science perspective? These can be very specific or more general. 


-   Given your to topic(s), where would you find data about it? Provide at least two sources, being as specific as possible. If you need to collect/scrape it yourself, describe the steps you'd need too take.


-   What challenges do you imagine having? How might you overcome them?  



-   Type your responses below and save it on Rmarkdown. 
A couple of topics I am interested in from a data science persepctive is soccer player recruitment, and also tactical analysis from coaches for set play routines.

I can find online the different ways in which teams recruit, and the different methods and datasetts they use to ensure they find the best players, or the best value players for their budget and positional needs.

I can find online the different ways in which teams recruit, and the different methods and datasetts they use to ensure they find the best players, or the best value players for their budget and positional needs.

It will be difficult to find the datasets they use because if they were public knowledge other teams would take advantage of them.